Insight Into Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-07-24 draft.tex
Reworked Structure with latest results

More than 5 variables are rarely analyzed simultaneously.
%%
%The variables analyzed simultaneously is limited to 
Our contributions are:
\begin{itemize}
	\item Analyzing back pain using image-derived variables of 2,240 subjects.
	\item Assessing the suitability of lumbar spine shape for diagnosing back pain
	\item Analyzing correlations between between image-based and socio-demographic as well as medical parameters.
\end{itemize}

@@

@@

\section{\uppercase{Materials and Method}}
\begin{figure}[!h]
  %\vspace{-0.2cm}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/age-gender}
  \caption{Age-Gender}
  \label{fig:example1}
 \end{figure}
\label{sec:MaterialsAndMethod}

\subsection{The Lumbar Spine Data Set}
Our data set compiled to analyze lumbar back pain comprises of 6,753 subjects from two cohorts (4,420 from \texttt{SHIP-Trend-0} and 2,333 from \texttt{SHIP-2}).
%%

%%

\subsubsection{Image Data}
\com{From VIS'14 Paper}
The lumbar spine was detected in the image data using a hierarchical finite element method by Rak et al. [32]. This semiautomatic method requires the user to initialize the tetrahedron-based finite element models (FEM) with a click on the L3 vertebra. Two user-defined landmarks on the top and bottom of the L3 vertebra describe an initial model height estimation. The model uses a weighted sum of T1and T2-weighted MR images to detect the lumbar spine shape. Once registered, it captures information about the shape of the lumbar spine canal as well as the position of the L1-L5 vertebrae [21]. Due to incorrect initialization, strongly deformed spines, contrast differences and artifacts, the model was not able to detect lumbar spines for all subjects. We obtained and worked with 2,540 tetrahedron models of the lumbar spine. For clustering, we extracted the centerline of the lumbar spine canal, which captures information about lordosis and scoliosis (the medical terms for spine curvature) [21].

\subsubsection{Non-Image Data}
\com{Analysis Using Heterogeneous Correlation}
The variables range from somatometric variables describing body measures to medical examinations, such as laboratory tests as well as lifestyle factors as sport activity or nutrition.

\subsection{Creating a Decision Tree using C5.0}
\com{C4.5 Algorithm for creating decision trees; }

\subsection{Parameter Assessment}

\section{\uppercase{Experiments}}
\label{sec:Experiments}
\subsection{Results}
\com{We can discriminate back pain using non-image data, but not with image-derived parameter}

@@

>>>>

More than 5 variables are rarely analyzed simultaneously.
%%
%The variables analyzed simultaneously is limited to 
Our contributions are:
\begin{itemize}
	\item Analyzing back pain using image-derived variables of 2,240 subjects.
	\item Assessing the suitability of lumbar spine shape for diagnosing back pain
	\item Analyzing correlations between between image-based and socio-demographic as well as medical parameters.
	\item Identification of most important variables using data mining methods \com{noch schoen schreiben}
	\item semiquantitative Auswertmöglichkeiten werden dem User oft zur verfügung gestellt
	\item Techniken sind als Teil des IVA-Frameworkes zu verstehen
\end{itemize}

@@

Risk factors for are not completely known, thus epidemiologists search for new correlations in cohort studies.

@@

\section{The Lumbar Spine Data Set}
\begin{figure}[!h]
  %\vspace{-0.2cm}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/age-gender}
  \caption{Age-Gender}
  \label{fig:example1}
 \end{figure}
\label{sec:MaterialsAndMethod}

Our data set compiled to analyze lumbar back pain comprises of 6,753 subjects from two cohorts (4,420 from \texttt{SHIP-Trend-0} and 2,333 from \texttt{SHIP-2}).
%%

%%
\subsection{Non-Image Data}
\com{Analysis Using Heterogeneous Correlation}
The variables range from somatometric variables describing body measures to medical examinations, such as laboratory tests as well as lifestyle factors as sport activity or nutrition.

\com{Es wurde mit einem weiten Spektrum Daten gesammelt, vom denen man glaubt, dass sie irgendwas mit der Wirbelsäulenverformung und dem Alterungsprozess zu tun haben. It is an active research area to determine these correlations.}

\subsection{Image Data}
\com{From VIS'14 Paper}
The lumbar spine was detected in the image data using a hierarchical finite element method by Rak et al. [32]. This semiautomatic method requires the user to initialize the tetrahedron-based finite element models (FEM) with a click on the L3 vertebra. Two user-defined landmarks on the top and bottom of the L3 vertebra describe an initial model height estimation. The model uses a weighted sum of T1and T2-weighted MR images to detect the lumbar spine shape. Once registered, it captures information about the shape of the lumbar spine canal as well as the position of the L1-L5 vertebrae [21]. Due to incorrect initialization, strongly deformed spines, contrast differences and artifacts, the model was not able to detect lumbar spines for all subjects. We obtained and worked with 2,540 tetrahedron models of the lumbar spine. For clustering, we extracted the centerline of the lumbar spine canal, which captures information about lordosis and scoliosis (the medical terms for spine curvature) [21].

%\subsection{Creating a Decision Tree using C5.0}
%\com{C4.5 Algorithm for creating decision trees; }

%\subsection{Parameter Assessment}
%Based on first results

@@

\subsection{Preliminary Results}
\begin{itemize}
	\item Direkter Vergleich
	\item Verteilung des Means
	\item Korrelationsmatrix
	\item PCA
\end{itemize}
Weil das nicht ausreichend war, haben wir einen C5.0 Baum erstellt, um alle potentiellen Zusammenhänge zwischen bildbezogenen und Nichtbildbezogenen Parametern herzustellen - Was kann man mit den Bilddaten erklären und was nicht?

\subsection{Experimental Settings and Results}
Decision Tree erklaeren, ebenfalls Umrechnen in die Dummy-Variablen. Was sind die Zielvariablen
\begin{itemize}
\item Altersgruppierung
\item Male/Female
\item Gewicht (BMI - dünn, normal, dick)
\end{itemize}
% Creating a Decision Tree using C5.0

%\com{C4.5 Algorithm for creating decision trees; }

\section{\uppercase{Evaluation of Decision Trees}}
\label{sec:Experiments}
\begin{itemize}
\item Vorgehen mit Scatterplot erklären
\item Beschreiben der Ergebnisse
\item Beschreiben des interaktiven Systems zum Anzeigen der Decision Trees
\end{itemize}

\com{We can discriminate back pain using non-image data, but not with image-derived parameter}
Welche parameter können wir gut unterscheiden
